---
title: "Data analysis of COVID-19 data set"
output: html_document
---
========================================================

<!-- useful links: -->
<!--     <https://projects.datacamp.com/projects/870> -->
<!-- <https://www.kaggle.com/kimjihoo/coronavirusdataset?select=TimeAge.csv> -->
<!-- <http://r-statistics.co/ggplot2-Tutorial-With-R.html#2.%20The%20Layers> -->
<!-- <http://r-statistics.co/Complete-Ggplot2-Tutorial-Part1-With-R-Code.html> -->




### Background info
    We make a structured dataset based on the report materials of KCDC and local governments.
    In Korea, we use the terms named '-do', '-si', '-gun' and '-gu',
    The meaning of them are explained below.

Levels of administrative divisions in South Korea:
    Upper Level (Provincial-level divisions)

    Special City: Seoul
    Metropolitan City: Busan / Daegu / Daejeon / Gwangju / Incheon / Ulsan
    Province(-do): Gyeonggi-do / Gangwon-do / Chungcheongbuk-do / Chungcheongnam-do / Jeollabuk-do / Jeollanam-do / Gyeongsangbuk-do / Gyeongsangnam-do

   Lower Level (Municipal-level divisions)

    City(-si) List of cities in South Korea
    Country(-gun) List of counties of South Korea
    District(-gu) List of districts in South Korea

### Libraries
```{r}
library(ggplot2)
library(data.table)
library(lubridate) # to work with dates and times
```

### Data load
```{r}
dt_case <- fread("data_set/Case.csv")
dt_patientinfo <- fread("data_set/PatientInfo.csv")
dt_policy <- fread("data_set/Policy.csv")
dt_region <- fread("data_set/Region.csv")
dt_SearchTrend <- fread("data_set/SearchTrend.csv")
dt_SeoulFloating <- fread("data_set/SeoulFloating.csv")
dt_TimeAge <- fread("data_set/TimeAge.csv")
dt_Time <- fread("data_set/Time.csv")
dt_TimeGender <- fread("data_set/TimeGender.csv")
dt_TimeProvince <- fread("data_set/TimeProvince.csv")
dt_weather <- fread("data_set/Weather.csv")
```

### Main part

## Anis

## Siyam

## Salim

## Aidin

### Playground

## Anis

## Siyam

## Salim

## Aidin
```{r}
all_provinces <- dt_case[, unique(province)] # list of unique provinces in SK
total_confirmed_cases <- numeric(0)
for ( prov in all_provinces ) {
  total_confirmed_cases[prov] <- dt_case[province == prov, sum(confirmed)]
}
dt_total_confirmed_cases <- data.table(province = all_provinces,    total_confirmed = total_confirmed_cases)
```
```{r}
ggplot(data = dt_total_confirmed_cases, aes(x= province, y = total_confirmed) ) + geom_point()
```
```{r}
ggplot(data = dt_TimeProvince, aes(x = date, y =confirmed, color = province )) + geom_line()
```
<br/>
Claim: Daegu has the most number of confirmed cases (= 6680).
We observe that in Daegu there were 6680 confirmed cases. Is it an outlier?
Let's try to understand why is that.

#### Daegu
##### How was the weather in Daegu compared to other provinces in this period (Jan - Jun)?
```{r}
weather_in_period <- dt_weather[code >= 10000]
ggplot(data = weather_in_period, aes(x = date, y = avg_temp, color = province ) ) + geom_line()
```
```{r}
ggplot(data = weather_in_period, aes(x = date, y = avg_temp, color = "Daegu" ) ) + geom_line()
ggplot(data = weather_in_period, aes(x = date, y = avg_relative_humidity, color = "Daegu" ) ) + geom_line()
```
<br/>
It seems that the weather does not play a role in this.

#### SearchTrend and Policies
```{r}
searchTrend_period <- dt_SearchTrend[date >= "2020-01-01"]  # to select from Jan-Jun
```
<br/>
To plot multiple columns with the same x-axis using ggplot we first need to transform the data table.
Using functions like melt, dcast, ...
```{r}
coord_x_date <- function(xlim = NULL, ylim = NULL, expand = TRUE) {
    if (!is.null(xlim)) {
        xlim <- lubridate::as_date(xlim)
    }
    ggplot2::coord_cartesian(xlim = xlim, ylim = ylim, expand = expand)
}
coord_x_datetime <- function(xlim = NULL, ylim = NULL, expand = TRUE) {
    if (!is.null(xlim)) {
        xlim <- lubridate::as_datetime(xlim)
    }
    ggplot2::coord_cartesian(xlim = xlim, ylim = ylim, expand = expand)
}
```
```{r}
melted_dt <- melt(searchTrend_period,  measure.vars = c("cold", "flu", "pneumonia", "coronavirus"), value.name = "search")
ggplot(data = melted_dt, aes(x = date, y =search, color = variable )) + geom_line()
  ## scale_x_date(date_breaks = "1 week") + coord_x_date( xlim = c("2020-01-01", "2020-04-01"))
```
Claim: People in SK heavily searched for keyword "coronavirus" among other words (cold, flu, pneumonia) is this period.

#### TimeSex
Claim: Over time the number of COVID-19 cases among females is greater than among males.
```{r}
ggplot(data = dt_TimeGender, aes(x=date, y=confirmed, color=sex)) + geom_line()
```
Look at the difference between F & M in time.
```{r}
cast_sex <- dcast(data = dt_TimeGender, formula  = date ~ sex, value.var = "confirmed" )
dt1 <- cast_sex[, .(difference_F_M = female - male), by = date]
dt1[, max(difference_F_M)] # maximal difference
ggplot(data = dt1, aes(x=date, y=difference_F_M)) + geom_line()
```
