---
title: "Data analysis of COVID-19 data set"
output: html_document
---
========================================================

### Background info
    We make a structured dataset based on the report materials of KCDC and local governments.
    In Korea, we use the terms named '-do', '-si', '-gun' and '-gu',
    The meaning of them are explained below.

Levels of administrative divisions in South Korea:
    Upper Level (Provincial-level divisions)

    Special City: Seoul
    Metropolitan City: Busan / Daegu / Daejeon / Gwangju / Incheon / Ulsan
    Province(-do): Gyeonggi-do / Gangwon-do / Chungcheongbuk-do / Chungcheongnam-do / Jeollabuk-do / Jeollanam-do / Gyeongsangbuk-do / Gyeongsangnam-do

   Lower Level (Municipal-level divisions)

    City(-si) List of cities in South Korea
    Country(-gun) List of counties of South Korea
    District(-gu) List of districts in South Korea

### Libraries
```{r}
library(ggplot2)
library(data.table)
```

### Data load
```{r}
dt_case <- fread("data_set/Case.csv")
dt_patientinfo <- fread("data_set/PatientInfo.csv")
dt_policy <- fread("data_set/Policy.csv")
dt_region <- fread("data_set/Region.csv")
dt_SearchTrend <- fread("data_set/SearchTrend.csv")
dt_SeoulFloating <- fread("data_set/SeoulFloating.csv")
dt_TimeAge <- fread("data_set/TimeAge.csv")
dt_Time <- fread("data_set/Time.csv")
dt_TimeGender <- fread("data_set/TimeGender.csv")
dt_TimeProvince <- fread("data_set/TimeProvince.csv")
dt_weather <- fread("data_set/Weather.csv")
```

### Main part

## Anis

## Siyam

## Salim

## Aidin


### Playground

## Anis

## Siyam

## Salim

## Aidin
