---
title: "Data analysis of COVID-19 data set"
output: pdf_document
---
========================================================

<!-- useful links: -->
<!--     <https://projects.datacamp.com/projects/870> -->
<!-- <https://www.kaggle.com/kimjihoo/coronavirusdataset?select=TimeAge.csv> -->
<!-- <http://r-statistics.co/ggplot2-Tutorial-With-R.html#2.%20The%20Layers> -->
<!-- <http://r-statistics.co/Complete-Ggplot2-Tutorial-Part1-With-R-Code.html> -->




### Background info
    We make a structured dataset based on the report materials of KCDC and local governments.
    In Korea, we use the terms named '-do', '-si', '-gun' and '-gu',
    The meaning of them are explained below.

Levels of administrative divisions in South Korea:
    Upper Level (Provincial-level divisions)

    Special City: Seoul
    Metropolitan City: Busan / Daegu / Daejeon / Gwangju / Incheon / Ulsan
    Province(-do): Gyeonggi-do / Gangwon-do / Chungcheongbuk-do / Chungcheongnam-do / Jeollabuk-do / Jeollanam-do / Gyeongsangbuk-do / Gyeongsangnam-do

   Lower Level (Municipal-level divisions)

    City(-si) List of cities in South Korea
    Country(-gun) List of counties of South Korea
    District(-gu) List of districts in South Korea

### Libraries
```{r}
library(ggplot2)
library(data.table)
library(lubridate) # to work with dates and times
library(dplyr)
library(bit64)

```

### Data load
```{r}
dt_case <- fread("data_set/Case.csv")
dt_patientinfo <- fread("data_set/PatientInfo.csv")
dt_policy <- fread("data_set/Policy.csv")
dt_region <- fread("data_set/Region.csv")
dt_SearchTrend <- fread("data_set/SearchTrend.csv")
dt_SeoulFloating <- fread("data_set/SeoulFloating.csv")
dt_TimeAge <- fread("data_set/TimeAge.csv")
dt_Time <- fread("data_set/Time.csv")
dt_TimeGender <- fread("data_set/TimeGender.csv")
dt_TimeProvince <- fread("data_set/TimeProvince.csv")
dt_weather <- fread("data_set/Weather.csv")
```

### Main part

# Claim 1: Daegu has the most number of confirmed cases (= 6680).
```{r}
all_provinces <- dt_case[, unique(province)] # list of unique provinces in SK
total_confirmed_cases <- numeric(0)
for ( prov in all_provinces ) {
  total_confirmed_cases[prov] <- dt_case[province == prov, sum(confirmed)]
}
dt_total_confirmed_cases <- data.table(province = all_provinces,    total_confirmed = total_confirmed_cases)
```

```{r}
ggplot(data = dt_total_confirmed_cases, aes(x= total_confirmed, y = province ) ) + geom_point()
```
```{r}
ggplot(data = dt_TimeProvince, aes(x = date, y =confirmed, color = province )) + geom_line()
```
<br/>
Comment: We observe that in Daegu there were 6680 confirmed cases. Is it an outlier?
Let's try to understand why is that.
[report](https://uclg-aspac.org/wp-content/uploads/2020/07/FinalOvercoming-COVID-19-in-Daegu_Korea_July-2020.pdf)


# Claim 2: Almost 50% of the total confirmed cases were originated from churches
```{r}
total_confirmed_cases <- dt_case[, list(total_confirmed_cases = sum(confirmed))]
print(total_confirmed_cases)
```
```{r}
# Data table with only the infection cases containing the keyword church
dt_case_related_to_churches <- dt_case[infection_case %like% "Church|church"]
head(dt_case_related_to_churches)
```
```{r}
# Total number of Cases orginated from the infection cases which contain the keyword 'Church' in it
total_cases_from_churches <- dt_case_related_to_churches[infection_case %like% "Church|church", list(total_cases = sum(confirmed))]
print(total_cases_from_churches)
```
```{r}
# Total number of infection cases caused from other sources
total_cases_from_other_sources <- dt_case[!infection_case %like% "Church|church", list(total_cases = sum(confirmed))]
print(total_cases_from_other_sources)
```
```{r}
# Proportion of the total cases originated from churches
proportion <- (total_cases_from_churches[, total_cases] / total_confirmed_cases[, total_confirmed_cases]) * 100
print(proportion)
```

```{r}
church <- data.table(infectionCases = c('From Church', 'Other Sources'), totalCount = c(total_cases_from_churches, total_cases_from_other_sources))

ggplot(church, aes(infectionCases, totalCount)) +
  geom_col()
```

```{r}
# Which church originated the highest number of infections
church_wise_cases <- dt_case_related_to_churches[, list(total_cases = sum(confirmed)), by = infection_case] %>%
  arrange(desc(total_cases))
church_wise_cases

ggplot(church_wise_cases, aes(infection_case, total_cases)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```



# Claim 3: The Patient who infected the most other patients
<!-- ```{r} -->
<!-- patient_with_most_infection_record <- dt_patientinfo[infected_by != "", list(inf_count = .N), by = infected_by] %>% arrange(desc(inf_count)) -->
<!-- patient_with_most_infection_record -->
<!-- ``` -->
<!-- ```{r} -->
<!-- id <- patient_with_most_infection_record[inf_count == max(inf_count), infected_by] -->
<!-- id -->
<!-- dt_patientinfo[patient_id == id] -->
<!-- ``` -->

# Claim 4: Claim regarding Death Cases Genderwise
#### Death cases are higher in males than females in general
### Affected vs Death numbers
```{r}
dt_patientinfo <- na.omit(dt_patientinfo, cols = "state")

# Let's first find the total affected people gender wise
total_affected_gender_wise <- dt_patientinfo[sex != "", list(count = .N), by = sex]
total_affected_gender_wise
```

```{r}
# Let's find out the total number of deceased people
total_deceased <- dt_patientinfo[state == "deceased", list(dount = .N)]
total_deceased
```

```{r}
# Now, find out the death count between males and females
total_death_gender_wise <- dt_patientinfo[state == "deceased" & sex != "", list(death_count = .N), by = sex] %>%
  arrange(desc(death_count))
total_death_gender_wise
```
### The most affected male age groups are from 60s - 80s
```{r}
# Now, find out the death count among MALES in different age groups
male_death_age_group_wise <- dt_patientinfo[state == "deceased" & sex == "male" & age != "", list(death_count = .N), by = age] %>% arrange(desc(death_count))
male_death_age_group_wise

ggplot(male_death_age_group_wise, aes(age, death_count)) +
  geom_col()
```
### The most affected female age groups are from 70s - 80s
```{r}
# Let's find out the death count among FEMALES in different age groups
female_death_age_group_wise <- dt_patientinfo[state == "deceased" & sex == "female" & age != "", list(death_count = .N), by = age] %>% arrange(desc(death_count))
female_death_age_group_wise


ggplot(female_death_age_group_wise, aes(age, death_count)) +
  geom_col()
```



```{r}
# Now, let's find out the number of affected people in different age groups in Males (We will ignore the empty ages)
male_affected_age_group_wise <- dt_patientinfo[age != "" & sex == "male", list(count = .N), by = list(age)] %>%
  arrange(desc(count))
male_affected_age_group_wise

ggplot(male_affected_age_group_wise, aes(age, count)) +
  geom_col()
```


```{r}
# Let's do the same for the females
female_affected_age_group_wise <- dt_patientinfo[age != "" & sex == "female", list(count = .N), by = list(age)] %>%
  arrange(desc(count))
female_affected_age_group_wise

ggplot(female_affected_age_group_wise, aes(age, count)) +
  geom_col()
```
```{r}
# Group wise affected and death case comparison for FEMALES
female_merged_affected_death <- merge(female_affected_age_group_wise, female_death_age_group_wise, by = "age", all.x = TRUE)
## female_merged_affected_death

female_merged_affected_death[, death_to_affected_proportion := (death_count / count) * 100]
## female_merged_affected_death
```

```{r}
# Group wise affected and death case comparison for MALES
male_merged_affected_death <- merge(male_affected_age_group_wise, male_death_age_group_wise, by = "age", all.x = TRUE)
male_merged_affected_death

male_merged_affected_death[, death_to_affected_proportion := (death_count / count) * 100]
male_merged_affected_death
```
```{r}
# Investigating the overall death to affected ratio gneder wise
merged_both_gender_death_and_affected <- merge(total_affected_gender_wise, total_death_gender_wise)
merged_both_gender_death_and_affected[, death_to_affected_proportion := (death_count/count) * 100]
merged_both_gender_death_and_affected
```

Comment: Although females are more affected but the death rate is almost twice in males than females

# Claim 5: Recovery time: Recovery time is the highest for the age group of 100s. It is both evident from the mean and median recovery time for each age group. However, the age group with the least recovery time varies in mean and median recovery time by age groups.

Recovery time is calculated as following:
recovery time = released_date - confirmed_date
```{r}
# Mean Recovery time by age groups
mean_recovery_time_by_age_groups <- dt_patientinfo[state == "released" & age != "", list(mean_recovery_time = mean(released_date - confirmed_date, na.rm = TRUE)), by = age] %>%
  arrange(desc(mean_recovery_time))
print(mean_recovery_time_by_age_groups)

ggplot(mean_recovery_time_by_age_groups, aes(x = age, y = mean_recovery_time)) +
  geom_col()
```

```{r}
# Median Recovery time by age groups

median_recovery_time_by_age_groups <- dt_patientinfo[state == "released" & age !="", list(median_recovery_time = as.double(median(released_date - confirmed_date, na.rm = TRUE))), by = age] %>% arrange(desc(median_recovery_time))

print(median_recovery_time_by_age_groups)

ggplot(median_recovery_time_by_age_groups, aes(x = age, y = median_recovery_time)) +
  geom_col()
```

```{r}
# Let's investigate the 0s age group
dt_0s_age_group <- dt_patientinfo[age == '0s' & age != "", list(mean = mean(released_date - confirmed_date, na.rm = TRUE), sD = sd(released_date - confirmed_date, na.rm = TRUE))]

dt_0s_age_group
```


```{r}
dt_10s_age_group <- dt_patientinfo[age == '10s' & age != "", list(mean = mean(released_date - confirmed_date, na.rm = TRUE), sD = sd(released_date - confirmed_date, na.rm = TRUE))]


dt_10s_age_group

```

# Claim 6 : People in SK heavily searched for keyword "coronavirus" among other words (cold, flu, pneumonia) is this period.
```{r}
searchTrend_period <- dt_SearchTrend[date >= "2020-01-01"]  # to select from Jan-Jun
```
<br/>
To plot multiple columns with the same x-axis using ggplot we first need to transform the data table.
Using functions like melt, dcast, ...
```{r}
coord_x_date <- function(xlim = NULL, ylim = NULL, expand = TRUE) {
    if (!is.null(xlim)) {
        xlim <- lubridate::as_date(xlim)
    }
    ggplot2::coord_cartesian(xlim = xlim, ylim = ylim, expand = expand)
}
coord_x_datetime <- function(xlim = NULL, ylim = NULL, expand = TRUE) {
    if (!is.null(xlim)) {
        xlim <- lubridate::as_datetime(xlim)
    }
    ggplot2::coord_cartesian(xlim = xlim, ylim = ylim, expand = expand)
}
```
```{r}
melted_dt <- melt(searchTrend_period,  measure.vars = c("cold", "flu", "pneumonia", "coronavirus"), value.name = "search")
ggplot(data = melted_dt, aes(x = date, y =search, color = variable )) + geom_line()
  ## scale_x_date(date_breaks = "1 week") + coord_x_date( xlim = c("2020-01-01", "2020-04-01"))
```


# Claim 7: the most effective measures against the number of covid cases were the immigration, technology, health policies (from February to March), education, alert, health and social measures (from March to April)
```{r}
class(dt_policy$start_date)
class(dt_Time$date)
class(dt_Time$ln_confirmed)
dt_policy$start_date <- as.Date(dt_policy$start_date, '%m/%d/%y', optional = FALSE)
dt_Time[, log_confirmed := log(confirmed, base = 10)]
dt_Time$ln_confirmed <- as.numeric(dt_Time$ln_confirmed)

ggplot(dt_policy, aes(x = start_date)) + geom_bar(width = 0.5, color = 'blue') + facet_wrap(~type, scales='free') + geom_line(data = dt_Time, aes(x = date , y = log_confirmed, color = 'red'))+ labs(title = "Number of Policies starting (by type) and daily log cumulated confirmed cases", x = "Months", y = "Count", font.title=2, font.x=0.1, font.y=1) + scale_x_date(breaks = "1 month", labels = date_format("%m"))
```
# Claim 8: higher average temperature induced more number of daily non group covid cases (May to June 2020) but had no clear relation with the number of daily group covid cases
```{r}
#Setup
dt_patientclean <- dt_patientinfo[!(is.na(dt_patientinfo$infection_case) | dt_patientinfo$infection_case==""), ]
dt_patientnongroup <- subset(dt_patientclean, dt_patientclean$infection_case == c("contact with patient", "overseas inflow", "etc"))
dt_patientgroup <- dt_patientclean[dt_patientclean$infection_case!="contact with patient",]
dt_patientgroup <- dt_patientgroup[dt_patientgroup$infection_case!="overseas inflow",]
dt_patientgroup <- dt_patientgroup[dt_patientgroup$infection_case!="etc",]
dt_patientnongrouptest <- dt_patientnongroup[dt_patientnongroup$infection_case!="overseas inflow",]
#average temperature & group=false
dt_weather$date <- as.Date(dt_weather$date, '%m/%d/%y', optional = FALSE)
dt_patientnongroup$confirmed_date <- as.Date(dt_patientnongroup$confirmed_date, '%m/%d/%y', optional = FALSE)

ggplot(dt_patientnongroup, aes(x = confirmed_date)) + geom_bar(width=0.5, color='blue') + geom_point(data = dt_weather, aes(x = date, y = avg_temp, color='red'))+ geom_smooth(data = dt_weather, aes(x = date, y = avg_temp)) + scale_x_date(breaks = "1 month",labels = date_format("%m-%Y"), limits = as.Date(c('2020-01-30', '2020-06-30'))) + labs(title = "Daily average temperature and daily non-group covid cases among patients in South-Korea", x = "Months", y = "Count", font.title=2, font.x=0.1, font.y=1)

#avg_temp & group=TRUE
ggplot(dt_patientgroup, aes(x = confirmed_date)) + geom_bar(width=0.5, color='blue') + geom_point(data = dt_weather, aes(x = date, y = avg_temp, color='red'))+ geom_smooth(data = dt_weather, aes(x = date, y = avg_temp)) + scale_x_date(breaks = "1 month",labels = date_format("%m-%Y"), limits = as.Date(c('2020-01-30', '2020-06-30'))) + labs(title = "Daily average temperature and daily group covid cases among patients in South-Korea", x = "Months", y = "Count", font.title=2, font.x=0.1, font.y=1)
```

# Claim 9: The daily Corona Virus cases decreased after the imposition of Online classes policy.
```{r}
class(dt_policy$start_date)
dt_policy$start_date <- as.Date(dt_policy$start_date, '%m/%d/%y', optional = FALSE)
class(dt_policy$start_date)

dt_Time$diff <- ave(dt_Time$confirmed, FUN=function(x) c(0, diff(x)))
class(dt_Time$diff)
dt_Time$policy <- NA
class(dt_Time$policy)
dt_Time$policy <- as.numeric(dt_Time$policy)
class(dt_Time$policy)

dt_Time[dt_Time$date=="2020-04-09","policy"] <- 820

ggplot(dt_Time, aes(date,diff)) + geom_line(color = 'red') + geom_col(data=dt_Time, aes(date, policy)) + labs(title = "Daily new Covid cases in Korea before and after Online classes policy", x = "Months", y = "Daily Cases", font.title=2, font.x=0.1, font.y=1)
```







Number of
```{r}
no_of_cases_day_wise <- dt_patientinfo[, list(affected_count = .N), by = confirmed_date]
no_of_recoveries_day_wise <- dt_patientinfo[, list(recovery_count = .N), by = released_date]
no_of_deaths_day_wise <- dt_patientinfo[state == "deceased", list(death_count = .N), by = confirmed_date]

setnames(no_of_cases_day_wise, "confirmed_date", "date")
setnames(no_of_recoveries_day_wise, "released_date", "date")
setnames(no_of_deaths_day_wise, "confirmed_date", "date")

merged_affected_and_recovery <- merge(no_of_cases_day_wise, no_of_recoveries_day_wise, by = "date")

merged_affected_and_recovery <- merge(merged_affected_and_recovery, no_of_deaths_day_wise, by = "date")
merged_affected_and_recovery

ggplot(na.omit(merged_affected_and_recovery), aes(x = date)) +
  geom_line(aes(y = affected_count), color = "darkred") +
  geom_line(aes(y = recovery_count), color = "steelblue", linetype = "twodash") +
  geom_line(aes(y = death_count), color = "darkgreen") +
  labs(colour = colnames(merged_affected_and_recovery))

```
